---
title: "bootstrapping"
author: "Xuehan Yang"
date: "2021/11/23"
output: github_document
---

repeated sample 

bootstrap is to mimic repeated sampling with the one sample you have.
bootstrap sample has the same size as the original sample, and is drawn with replacement.

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Bootstrapping in SLR

```{r}
n_samp = 250

sim_df_const = 
  tibble(
    x = rnorm(n_samp, 1, 1),
    error = rnorm(n_samp, 0, 1),
    y = 2 + 3 * x + error
  )

sim_df_nonconst = sim_df_const %>% 
  mutate(
  error = error * .75 * x,
  y = 2 + 3 * x + error
)
```

One case in which the usual linear regression assumptions hold and one case in which they don’t. The plot below illustrates the differences between the dataset.

```{r}
sim_df = 
  bind_rows(const = sim_df_const, nonconst = sim_df_nonconst, .id = "data_source") 

sim_df %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm") +
  facet_grid(~data_source)
```


```{r}
lm(y ~ x, data = sim_df_const) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

```{r}
lm(y ~ x, data = sim_df_nonconst) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```


Lets try to use the bootstrap for inference

```{r}
bootstrap_sample =
  sim_df_nonconst %>% 
  sample_frac(size = 1, replace = TRUE) %>% 
  arrange(x)

lm(y~x, data = bootstrap_sample)
```

lets write a function

```{r}
boot_sample = function(df){
  
  sample_frac(df, size = 1, replace = TRUE)
  
}
```

```{r}
boot_sample(sim_df_nonconst) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm")
```

Drawing many bootstrap samples

```{r}
boot_straps = 
  data_frame(
    strap_number = 1:1000,
    strap_sample = rerun(1000, boot_sample(sim_df_nonconst))
  )

boot_straps
```

```{r}
boot_straps %>% 
  filter(strap_number %in% 1:2) %>% 
  mutate(strap_sample = map(strap_sample, ~arrange(.x, x))) %>% 
  pull(strap_sample)
```

```{r}
boot_straps %>% 
  filter(strap_number %in% 1:3) %>% 
  unnest(strap_sample) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_point(alpha = .5) +
  stat_smooth(method = "lm", se = FALSE) +
  facet_grid(~strap_number) 
```

Analyzing bootstrap samples

```{r}
bootstrap_results = 
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(results) 
```

```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate)) %>% 
  knitr::kable(digits = 3)
```

```{r}
bootstrap_results %>% 
  group_by(term) %>% 
  summarize(
    ci_lower = quantile(estimate, 0.025), 
    ci_upper = quantile(estimate, 0.975))
```

```{r}
boot_straps %>% 
  unnest(strap_sample) %>% 
  ggplot(aes(x = x, y = y)) + 
  geom_line(aes(group = strap_number), stat = "smooth", method = "lm", se = FALSE, alpha = .1, color = "blue") +
  geom_point(data = sim_df_nonconst, alpha = .5)
```

bootstrap

```{r}
boot_straps = 
  sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000)

boot_straps$strap[[1]]

as_data_frame(boot_straps$strap[[1]])
```

```{r}
sim_df_nonconst %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~lm(y ~ x, data = .x) ),
    results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

```{r}
sim_df_const %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(models = map(strap, ~lm(y ~ x, data = .x) ),
         results = map(models, broom::tidy)) %>% 
  select(-strap, -models) %>% 
  unnest(results) %>% 
  group_by(term) %>% 
  summarize(boot_se = sd(estimate))
```

Airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  drop_na(price, stars) %>% 
  select(price, stars, borough, neighborhood, room_type)
```

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price, color = room_type)) + 
  geom_point()
```

```{r}
nyc_airbnb %>% 
  filter(borough == "Manhattan") %>% 
  modelr::bootstrap(n = 1000) %>% 
  mutate(
    models = map(strap, ~ lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)) %>% 
  select(results) %>% 
  unnest(results) %>% 
  filter(term == "stars") %>% 
  ggplot(aes(x = estimate)) + geom_density()
```







