---
title: "crossvalidation"
author: "Xuehan Yang"
date: "2021/11/18"
output: github_document
---

Although hypothesis tests provide a way to compare nested linear models, in many situations the approaches under consideration don’t fit nicely in this paradigm. Indeed, for many modern tools and in many applications, the emphasis lies on prediction accuracy rather than on statistical significance. In these cases, cross validation provides a way to compare the predictive performance of competing methods.

```{r}
library(tidyverse)
library(modelr)
library(mgcv)
library(viridis)



knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## CV "by hand", Simulate a dataset

```{r}
set.seed(1)

nonlin_df = tibble(
  id = 1:100,
  x  = runif(100, 0, 1),
  y  = 1 - 10*(x - .3)^2 + rnorm(100, 0, .3)  
)

nonlin_df %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point()
```

Create splits by hand, plot, fit models

```{r}
train_df = sample_n(nonlin_df, 80)
test_df = anti_join(nonlin_df, train_df, by = "id")

ggplot(train_df, aes(x = x, y = y)) +
  geom_point() +
  geom_point(data = test_df, color = "red")

```

Fit my models.

```{r}
linear_mod = lm(y ~ x, data = train_df)
smooth_mod = mgcv::gam(y ~ s(x), data = train_df)
wiggly_mod = mgcv::gam(y ~ s(x, k = 30), sp = 10e-6, data = train_df)
```

Plot the results

```{r}
train_df %>% 
  add_predictions(smooth_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred))
```

```{r}
train_df %>% 
  add_predictions(wiggly_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred))
```

```{r}
train_df %>% 
  add_predictions(linear_mod) %>% 
  ggplot(aes(x = x, y = y)) +
  geom_point() +
  geom_line(aes(y = pred))
```

quantify the results

```{r}
rmse(linear_mod, test_df)
rmse(smooth_mod, test_df)
rmse(wiggly_mod, test_df)
```




















