---
title: "linear_models"
author: "Xuehan Yang"
date: "2021/11/16"
output: github_document
---

```{r}
library(tidyverse)
library(p8105.datasets)

set.seed(1)
```

## Model fitting

```{r}
data("nyc_airbnb")

nyc_airbnb = nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2) %>% 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) %>% 
  filter(borough != "Staten Island") %>% 
  select(price, stars, borough, neighborhood, room_type)
```

Visualizations

```{r}
nyc_airbnb %>% 
  ggplot(aes(x = stars, y = price)) + geom_point()
```

Let's fit a linear model

```{r}
fit = lm(data = nyc_airbnb, price ~ stars + borough)
```

Being cirtical with factor
```{r}
nyc_airbnb = nyc_airbnb %>% 
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  )

fit = lm(data = nyc_airbnb, price ~ stars + borough)
```

## Tidying out

output of lm is an object of class lm.

```{r}
summary(fit)
summary(fit)$coef
coef(fit)
fitted.values(fit)
```

broom package has functions for obtaining a quick summary of the model and for the cleaning up the coefficient table.
output is a table
```{r}
fit %>% 
  broom::glance()
```

```{r}
fit %>% 
  broom::tidy()
```

```{r}
fit %>% 
  broom::tidy() %>% 
  select(term, estimate, p.value) %>% 
  mutate(term = str_replace(term, "^borough", "Borough: ")) %>% 
  knitr::kable(digits = 3)
```

Diagnostics

detect any failues in model assumptions

```{r}
modelr::add_residuals(nyc_airbnb, fit)
```

```{r}
modelr::add_predictions(nyc_airbnb, fit)
```

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin()
```

```{r}
nyc_airbnb %>% 
  modelr::add_residuals(fit) %>% 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()
```

## Hypothesis testing

```{r}
fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alt = lm(price ~ stars + borough + room_type, data = nyc_airbnb)
```

```{r}
anova(fit_null, fit_alt) %>% 
  broom::tidy()
```

this anova is only used to assess nested model. For non-nested model, using cross-validatoin

## Nesting data

fitting models to datasets nested within variables.

```{r}
nyc_airbnb %>% 
  lm(price ~ stars*borough + room_type*borough, data = .) %>% 
  broom::tidy() %>% 
  knitr::kable(digits = 3)
```

```{r}
nest_lm_res = 
  nyc_airbnb %>% 
  nest(data = -borough) %>% 
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(
    -data, -models
  ) %>% 
  unnest(results)
```

the expected change in price comparing an entire apartment to a private room in Queens, for example, involves the main effect of room type and the Queens / private room interaction.

```{r}
nest_lm_res %>% 
  select(borough, term, estimate) %>% 
  mutate(term = fct_infreq(term)) %>% 
  pivot_wider(
    names_from = term,
    values_from = estimate
  ) %>% 
  knitr::kable(digits = 3)
```

```{r}
manhattan_airbnb = 
  nyc_airbnb %>% 
  filter(borough == "Manhattan")

manhattan_nest_lm_res = 
  manhattan_airbnb %>% 
  nest(data = -neighborhood) %>%
  mutate(
    models = map(data, ~lm(price ~ stars + room_type, data = .x)),
    results = map(models, broom::tidy)
  ) %>% 
  select(-data, -models) %>% 
  unnest(results)
```

```{r}
manhattan_nest_lm_res %>%
  filter(str_detect(term, "room_type")) %>% 
  ggplot(aes(x = neighborhood, y = estimate)) +
  geom_point() +
  facet_wrap(~term) +
  theme(axis.text.x = element_text(angle = 80, hjust = 1))
```

Binary Outcome--logistic regression

```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") %>% 
  filter(city == "Baltimore") %>% 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age),
    victim_race = fct_relevel(victim_race, "White")) %>% 
  select(resolved, victim_age, victim_race, victim_sex)
```

Fit a logistic regression

```{r}
fit_logistic = baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())
```

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(OR = exp(estimate)) %>% 
  select(term, log_OR = estimate, OR, p.value) %>% 
  knitr::kable(digits = 3)
```

```{r}
baltimore_df %>% 
  modelr::add_predictions(fit_logistic) %>% 
  mutate(fitted_prob = boot::inv.logit(pred))
```

